Introduction

### 2015-07-22 dissertation/papersincontext.tex
philosophy

Although the support for caching headers are not yet widespread, it is
sufficient to perform experiments on real-world data.

@@

>>>>

Although the support for caching headers is not yet widespread, it is
sufficient to perform experiments on real-world data.

@@

Dissatisfaction with the methodology used in the literature,
specifically benchmarking, to test assertions of performance lead to
exploration of statistical methods in referenced in
Section~\ref{sec:condoe}, and to organise the Empirical 2014 Workshop
at the Extended Semantic Web Conference (which I was unfortunately
prevented from attending myself). Still, frustrated by the slow
progress of the last 16 years, and difficulty with comparing methods
to the more mature natural sciences, I still felt the need to express
a philosophical view of science, which I did by submitting an article
to the ``Negative or inconclusive results in Semantic Web'' at the
Extended Semantic Web Conference 2015. The essay, see
\cite{kjernsmo_noise_2015} was tangential to the Call for Papers, but
the chairs decided that Jacco van Ossenbruggen would interview me in
front of the audience about the contents of this essay.

Again, the essay serves somewhat as an excuse for why the evaluations
in this dissertation does not meet the standards that I would
advocate, it would require many years of concerted effort to meet
those standards. The intention is then to promote a discussion of
epistemological questions, and as such, the essay is intentionally
provocative.  In retrospect, the greatest weakness of the essay is
that I failed to recognise the impact of Frank van Harmelen's call for
studies that can establish laws of the Semantic Web information
universe, as discussed in Section~\ref{sec:evalproblems}. To my
defence, I was only made aware of this keynote by the
reviewer.
